HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
mi

We conduct experiments with four language pairs: English-German, English-Polish,
English-Romanian and English-Czech, and report efficiency (time of annotation) and
inter-annotator agreement scores (\secref{sec:exps}). Efficiency results that HUME
can be annotated in 2--4 minutes, once the UCCA annotation of the source is given,
which is only about five times slower than MEANT, and hence still practical to
employ on a moderate scale. HUME's agreement results are on par with those
of standard sentence-level ranking measures, but unlike them,
HUME's scores do not decrease with longer sentences.\bh{We may
  have to focus more on qualitative aspects, if we just try to sell
  the measure on IAA, then the figures are not stunning. OA: is that OK?}

>>>>

We conduct experiments with four language pairs: English-German, English-Polish,
English-Romanian and English-Czech, and report efficiency (time of annotation) and
inter-annotator agreement scores (\secref{sec:experiments}). Efficiency results that HUME
can be annotated in 2--4 minutes, once the UCCA annotation of the source is given,
which is only about five times slower than MEANT, and hence still practical to
employ on a moderate scale. HUME's agreement results are on par with those
of standard sentence-level ranking measures, but unlike them,
HUME's scores do not decrease with longer sentences.\bh{We may
  have to focus more on qualitative aspects, if we just try to sell
  the measure on IAA, then the figures are not stunning. OA: is that OK?}
